manuscript_notes

### 2024-11-06 notes/manuscript_notes.Rmd
update ms. and suppl. material.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

section 4.1.2
We mention life tables, but have we defined them before this point? If not, we need to define them first. And mention why they are important. If not, they just come out of nowhere.

indeed, maybe the below quoted text should come earlier to explain life tables

@@

@@

@@

@@

@@

@@

@@

@@

- model_M1. 
--The use of 0 and Intercept needs explaining.
--adapt_delta is high. I rarely have to go above 0.99. Does the model not look right if this is set lower? This could be a sign that the model is not a suitable structure.
--step_size - I have never set this. Can you send me some info on this parameter?
-- init set at exactly zero. This should be avoided whenever possible. Try init_r = 0.1. This means that the start points will vary between -0.1 and 0.1, rather than always being the same value (zero).
-- Although condition is defined earlier. I would make it clear in this section what condition means, as it is super important.

- model_M2
-- clearly define what period_9 means.
-- It seems to me that you have quadratic and 3rd order terms, but you only mention 3rd order in the text.

@@

@@

>>>>

-> I replaced each reaction with response, as reaction is often used for detection tasks only.

@@

-> Yes, I will check the bib file... correct version is in extrareferences.bib (backup for extrareferences2.bib)

@@

-> ref papaja is in extrareferences.bib

@@

-> removed equation numbers in sections 2 and 2..

@@

-> yes, done.

@@

-> I removed it, and added it with explanation in the supplementary material - part A.

@@

-> Deleted and moved to supplementary material.

@@

-> Sentence deleted, but wrapped with old paragraph in figure legend of Figure 2.

@@

-> The prime is presented *before* the target. I removed the minus and made it explicit.

@@

-> great.

@@

-> I clearly explained it..... todo

@@

-> I expected problems with fitting the very complex model M4. But even M3 has problems.

@@

-> added in

@@

-> I prefer the last option. I created a new figure 3.

@@

section 4.1.2
We mention life tables, but have we defined them before this point? If not, we need to define them first. And mention why they are important. If not, they just come out of nowhere.
indeed, maybe the below quoted text should come earlier to explain life tables

@@

-> Done.  todo...

@@

-> Done.  todo....

@@

-> I think it is important for naive readers to get an idea of how the variables in the models presented later are calculated.

@@

-> adapt-delta of 0.999 is not unusual for generalized linear mixed models.

@@

-> Done todo

@@

-> done todo

@@

-> Explanation for large values is given in the table captions.  todo

@@

- model_M1. 
--The use of 0 and Intercept needs explaining.

-> done.

--adapt_delta is high. I rarely have to go above 0.99. Does the model not look right if this is set lower? This could be a sign that the model is not a suitable structure.

--step_size - I have never set this. Can you send me some info on this parameter?
-- init set at exactly zero. This should be avoided whenever possible. Try init_r = 0.1. This means that the start points will vary between -0.1 and 0.1, rather than always being the same value (zero).

-- Although condition is defined earlier. I would make it clear in this section what condition means, as it is super important.

-> Done... todo

- model_M2
-- clearly define what period_9 means.

-- It seems to me that you have quadratic and 3rd order terms, but you only mention 3rd order in the text.

-> I thought a "third order polynomial" implies a constant, linear, quadratic and cubic component...

@@

-> todo.  Done....

@@

-> I prefere option 1, and added a new subsection... todo
